---
title: "Leaflet"
author: "Tomas Fuenzalida"
date: "2 de junio de 2020"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Leaflet

###Primer Mapa

Permite la creacion de graficos con mapas y otras cosas al igual que googlevis

```{r, eval = FALSE}
library(leaflet)
my_map <- leaflet() %>% addTiles()
#La notacion %>% (piping) entrega el output "my_map" como el primer elemento de la siguiente funcion
my_map
```

###Add Marks

```{r, eval = FALSE}
my_map <- my_map %>% addMarkers(lat = 39.2980803, lng = -76.5898801, popup = "Jeff Leek Offices")
my_map
```

###Add Various points

```{r, eval = FALSE}
set.seed(2016-04-25)
df <- data.frame(lat = runif(20, min = 39.2, max  = 39.3),
                 lng = runif(20, min = -76.7, max = -76.5),
                 popup = 1:20)
df %>%
        leaflet() %>% 
        addTiles() %>% 
        addMarkers(popup = ~as.character(popup))
```

## Making Custom Marks

```{r, echo=FALSE}
hopkinsIcon <- makeIcon(
  iconUrl = "http://brand.jhu.edu/content/uploads/2014/06/university.shield.small_.blue_.png",
  iconWidth = 31*215/230, iconHeight = 31,
  iconAnchorX = 31*215/230/2, iconAnchorY = 16
)

hopkinsLatLong <- data.frame(
  lat = c(39.2973166, 39.3288851, 39.2906617, 39.2970681, 39.2824806),
  lng = c(-76.5929798, -76.6206598, -76.5469683, -76.6150537, -76.6016766))

hopkinsLatLong %>% 
  leaflet() %>%
  addTiles() %>%
  addMarkers(icon = hopkinsIcon)
```

## Adding Multiple Popups

```{r, echo=FALSE}
hopkinsSites <- c(
  "<a href='http://www.jhsph.edu/'>East Baltimore Campus</a>",
  "<a href='https://apply.jhu.edu/visit/homewood/'>Homewood Campus</a>",
  "<a href='http://www.hopkinsmedicine.org/johns_hopkins_bayview/'>Bayview Medical Center</a>",
  "<a href='http://www.peabody.jhu.edu/'>Peabody Institute</a>",
  "<a href='http://carey.jhu.edu/'>Carey Business School</a>"
)

hopkinsLatLong %>% 
  leaflet() %>%
  addTiles() %>%
  addMarkers(icon = hopkinsIcon, popup = hopkinsSites)
```

## Mapping Clusters

Sometimes you might have so many points on a map that it
doesn't make sense to plot every marker. In these situations
leaflet allows you to plot clusters of markers using
`addMarkers(clusterOptions = markerClusterOptions())`. When
you zoom in to each cluster, the clusters will separate until
you can see the individual markers.

```{r, eval=FALSE}
df <- data.frame(lat = runif(500, min = 39.25, max = 39.35),
                 lng = runif(500, min = -76.65, max = -76.55))
df %>% 
  leaflet() %>%
  addTiles() %>%
  addMarkers(clusterOptions = markerClusterOptions())