---
title: "Improving people's training"
author: "Tomas Fuenzalida"
date: "29 de mayo de 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Objetive

The objective of this project is to put into practice the knowledge acquired in the Machine Learning course, part of the Data Science specialization in coursera taught by John Hopkins University.
For this, the data delivered by different devices will be used when performing a physical exercise on different people, which will be rated according to the technique used. With these observations, a classification model will be calibrated that allows estimating 20 observations that have not been classified.

##Background

Using devices such as Jawbone Up, Nike FuelBand, and Fitbit it is now possible to collect a large amount of data about personal activity relatively inexpensively. These type of devices are part of the quantified self movement – a group of enthusiasts who take measurements about themselves regularly to improve their health, to find patterns in their behavior, or because they are tech geeks. One thing that people regularly do is quantify how much of a particular activity they do, but they rarely quantify how well they do it. In this project, your goal will be to use data from accelerometers on the belt, forearm, arm, and dumbell of 6 participants. They were asked to perform barbell lifts correctly and incorrectly in 5 different ways. More information is available from the website here: http://web.archive.org/web/20161224072740/http:/groupware.les.inf.puc-rio.br/har (see the section on the Weight Lifting Exercise Dataset).

##Data

The training data for this project are available here:

https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv

The test data are available here:

https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv

The data for this project come from this source: http://web.archive.org/web/20161224072740/http:/groupware.les.inf.puc-rio.br/har. If you use the document you create for this class for any purpose please cite them as they have been very generous in allowing their data to be used for this kind of assignment.

## Download, Pre-process and analisis Data

```{r, results='hide', error = FALSE, warning=FALSE, message=FALSE}
library(dplyr)
library(ggplot2)
library(caret)
```

Download the training dataset

```{r Download Data}
data <- read.table("pml-training.csv", header = TRUE, sep = ",", na.strings = c("","NA"))
```

I remove the variables that do not generate a contribution to a future model such as time

```{r Remove Variables}
data <- data[,-c(1,3,4,5,6,7)]
```
I remove all the columns that have NA

```{r Remove columns with NA}
data <- data[ , colSums(is.na(data)) == 0]
```

To see possible relationships between the form of the exercise and the different research participants, we made a plot of the number of exercises qualified by each person

```{r Plot exercises by personas by classification}
g <- ggplot(data, aes(x = user_name, fill = classe))
g <- g + geom_bar(position = "dodge", col = "black");
g <- g + labs(title = "Excercise by Name and Classe", x = "Names", y = "Frecuency");
g <- g+ theme(plot.title = element_text(hjust = 0.5)); g
```

As it is possible to see in the previous graph, there is no relationship between the classification of the exercise and the person, so the user_name variable is eliminated

```{r Delete variable name}
data <- data[,-c(1)]
```

We create the data partition between my training data and my testing data.

```{r Data Partition}
inTrain <- createDataPartition(y = data$classe, p = 0.7, list = FALSE)
training <- data[inTrain,]
testing <- data[-inTrain,]
```

In order to better select the variables that can best explain the type of exercise being done, we seek to verify that all of these have minimal variability so that they deliver value to the model.

```{r near zero variable}
nearZeroVar(training,saveMetrics = TRUE)
```

As can be seen, there are no variables with variability close to 0, so we use all the variables and start pre-processing the data with the center and scaling method.

```{r Pre Procesess}
preobj <- preProcess(training, method = c("center","scale"))
training <- predict(preobj, training)
```

##Training the Model

Since the problem corresponds to one of classification, the "random forest" technique was used to tuiolize with 3 cross validations to reduce the computational load

```{r Training random forest, eval = FALSE}
mod1 <- train(classe ~ ., data = training, method = "rf", trControl = trainControl(method = "cv", number = 3))
```
```{r, results='hide', error = FALSE, warning=FALSE, message=FALSE, echo = FALSE}
load(file = "model training", verbose = TRUE)
```
```{r Predict and confusionmatrix}
pred1 <- predict(mod1,training)
confusionMatrix(pred1, training$classe)
```

After the model training, we perform the same sequence to the test data from the pre-process to the prediction.

```{r test_set}
preobj_testing <- preProcess(testing, method = c("center","scale"))
testing <- predict(preobj, testing)
pred2 <- predict(mod1,testing)
confusionMatrix(pred2, testing$classe)
```

##Select Model
```{r finalModel}
mod1$finalModel
```

We select this model as it has less than a 1% error which is strong enough to be an almost perfect model

#Predict data not found

The final test data is finally opened and used to predict the missing data

```{r Download Data6}
data_test <- read.table("pml-testing.csv", header = TRUE, sep = ",", na.strings = c("","NA"))
preobj_test <- preProcess(data_test, method = c("center","scale"))
data_test <- predict(preobj, data_test)
pred_test <- predict(mod1,data_test); pred_test
```

##Conclusion

In the framework of the Machine Learning project of the data science specialization of the John Hopkins University, the objective set out at the beginning of the document was achieved, managing to train a model robust enough that it could predict the type of exercise that was being carried out, achieving hit percentages of more than 99% and with this predicting perfectly in the test data